### 2020-05-14 cover-letter/cover-letter.Rmd
cover letter

---
from: Nicholas Tierney
fromqualifications: BPsySc (Hons), PhD (Statistics)
fromtitle: Lecturer
fromWWW: njtierney.com
fromemail: nicholas.tierney@gmail.com
fromphone: +61 3 9905 9352
fromsignature: sigfile.png
toname: Editor in Chief
toaddress: Journal of Statistical Software
opening: Dear Editors-in-Chief
closing: Regards, \newline Dr. Nicholas Tierney \newline Lecturer
spacing: 1.4
output: MonashEBSTemplates::letter
---

Please consider my article "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations" for possible publication in the Journal of Statistical Software. This article describes new work on handling missing values from a data centric approach. The methodology is implemented in the R package, `naniar`, which is available on CRAN, https://cran.r-project.org/web/packages/naniar, with the development version on github https://github.com/njtierney/naniar. `naniar` is now downloaded 14 thousand times a month, and has been downloaded over 160 thousand times. `naniar` has also seen wide praside, for example: [Karandeep Singh](https://twitter.com/kdpsinghlab/status/1110529278830170116):

@@

Along with the PDF is an accompanying Rmarkdown file, which contains all of the code to reproduce the results in this paper. This article is not under consideration elsewhere.  This paper was submitted two years aho to the Journal of Computational and Graphical Statistics, but was rejected. It has now been substantially re-written. We have submitted a pre-print of this article to arxiv, and to our internal department pre-print at Monash University.

We hope that you find this paper of interest to the readers of Journal of Statistiacl Software,

>>>>

---
from: Nicholas Tierney
fromqualifications: BPsySc (Hons), PhD (Statistics)
fromtitle: Lecturer
fromWWW: njtierney.com
fromemail: nicholas.tierney@gmail.com
fromphone: +61 3 9905 9352
fromsignature: sigfile.png
toname: Editors-in-Chief
toaddress: Journal of Statistical Software
opening: Dear Editors-in-Chief
closing: Regards, \newline Dr. Nicholas Tierney \newline Lecturer
spacing: 1.4
output: MonashEBSTemplates::letter
---

Please consider my article "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations" for publication in the Journal of Statistical Software. This article describes new work on handling missing values using a tidy approach. The methods are implemented in the R package, `naniar`, which is available on CRAN (https://cran.r-project.org/web/packages/naniar), and the development version is available on github https://github.com/njtierney/naniar. The package, `naniar` is being downloaded at a volume of 14,000 times a month, with total lifetime downloads 160,000 times, as measured from the RStudio server using the `cranlogs` package. The work has very visible, and widely praised, for example: [Karandeep Singh](https://twitter.com/kdpsinghlab/status/1110529278830170116) says:

@@

Along with the PDF is an accompanying Rmarkdown file, which contains all of the code to reproduce the results in this paper. This article is not under consideration elsewhere.  This paper was submitted two years ago to the Journal of Computational and Graphical Statistics, but was rejected. It has now been substantially re-written, based on reviewer feedback. We have submitted a pre-print of this article to arxiv, and to our internal department pre-print series at Monash University.

We hope that you find this paper of interest to the readers of Journal of Statistical Software,
